### 2017-03-01 readme.Rmd
added bias method after I fixed the bias_layer estimation.

Import some species data and covariates for modelling
```{r,message=FALSE}
library(sdm)
library(rgdal)
library(raster)

@@

>>>>

Import some species data and covariates for modelling
```{r,message=FALSE}
library(sdm)
library(raster)

@@

Here we can use the example data from above to set up a layer that will inform inclusion.probabilties for quasirandom background points. In this example, I'm using the absence data too, in reality you'd just construct a presence-absence model - but I thought it'd be fun to play with a bit more data.

```{r}
bias_layer <- eip(known_sites = species@coords,
                  study_area = preds[[1]],
                  sigma = 10000)

Now let's generate some back ground points using our bias layer
```{r}
bkpts_bias <- generate_background_points(number_of_background_points = 1000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    bias_layer = bias_layer,
                                    method = 'bias')

plot(preds[[1]])
points(bkpts_bias[bkpts_bias$presence==0,c("x","y")],cex=.5,pch=16)
```

Now let's try and fit a model. Looking pretty good and we only used 1000 background points. 
```{r}

fm4 <- gam(presence ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation) + 
              offset(log(weights)),
              data = bkpts_bias,
              family = poisson())

p4 <- predict(object=preds,
             model=fm4,
             type = 'response',
             const=data.frame(weights = 1))

p4_cell <- p4*(res(preds)[1]*res(preds)[2])

plot(p4_cell)
```
